---
title: "Splot: Quite the Useless Shiny App"
author: "Qubixes"
date: "11/21/2018"
output: slidy_presentation
framework: revealjs
revealjs: {theme: moon}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

Splot is a toy application published on shinyapps.io. It's use is limited, except for the educational purposes of the author. Personally, I think 5 pages is way too much, so let's just stretch it out... 

## Purpose and features

- Visualizing the *mtcars* data set.
- Fiting a linear spline.
- Different x-axis (hp, cyl, disp, wt)
- Use different factors such as (cyl, am) as colors of the points.
- Get a F-statistic to find the best breaking point of the spline.

## Server code

```{r cars, echo = FALSE}
library(shiny)
library(ggplot2)
data("mtcars")
```

The client code is quite uninteresting, so let's assume we loaded everything into the input variable:

```{r, echo=TRUE}
input = list(xbreak=150, xval="hp", col="cyl")
```

Then we have a (reactive) function that fits the model and returns a model with the linear spline and the data frame:

```{r, echo=TRUE}
    modelFit <- function(){
        xspl <- ifelse(mtcars[,input$xval]>input$xbreak, mtcars[,input$xval]
                       -input$xbreak, 0)
        modelDF <- data.frame(mpg=mtcars$mpg, x=mtcars[,input$xval], 
                              ones=rep(1,dim(mtcars)[1]), xspl=xspl)
        list(lm(mpg~x+xspl+ones-1, data=modelDF), modelDF)
    }
```



## The PLOT

The plot is made using ggplot2, and with the previous values for the input we get:

```{r, echo = FALSE}
  mod <- modelFit()
mydf <- data.frame(mod[[2]], ypred=suppressWarnings(predict(mod[[1]], mod[[2]])), col=factor(mtcars[,input$col]))
      ggplot(data=mydf, aes(x=x, y=mpg))+
        geom_point(aes(color=col))+
        geom_line(color='blue', data=mydf, aes(x=x, y=ypred))+
        labs(x=input$xval, colour=input$col)
```

